### 2019-10-11 paper/introduction.tex

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not
exist in the Earth's crust and can be produced from fertile $^{232}$Th only in
the nuclear reactor. Therefore, it is required to examine alternative fissile
materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time\footnote{Time required to produce enough amount of $^{233}$U to trigger a
new SD-TMSR.} of $^{233}$U because in this case all startup fissile material
is being substituted by newly produced $^{233}$U.

Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source to 
$^{233}$U because it has the highest ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for
the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approache tends to store produced $^{233}$U out of the 
core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
as startup fuel. They concluded that the transition to thorium fuel cycle can
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

@@

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling,
ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
heuer2014towards,fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed scenarios were selected:

@@

This present paper is organized as follows: after an introduction about 
\gls{MSR} systems, the model description is discussed in section 2. 
Methodology and tools is descried in section 3. Extraction and feed mechanisms 
are addressed in section 4. Section 5 focuses on the results and discussion. 
Finally, section 6 highlights the conclusions.

>>>>

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start-up new \glspl{MSR}. But $^{233}$U does not
exist in the Earth's crust and can be produced from fertile $^{232}$Th only in
the nuclear reactor. Therefore, it is required to examine alternative fissile
materials (e.g., $^{235}$U) to replace the $^{233}$U in the start-up fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time\footnote{Time required to produce enough amount of $^{233}$U to trigger a
	new SD-TMSR.} of $^{233}$U because in this case all start-up fissile material
is being substituted by newly produced $^{233}$U.

Betzler \emph{et al.} discussed the simulation of the start-up of a MSBR unit
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source to 
$^{233}$U because it has the highest ratio of fissile isotopes
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for
the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
(2) ex-core transition. In the first approach, the TMSR is launched with 
existing fissile material and thorium as a fertile material; then the 
$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
In contrast, the second approache tends to store produced $^{233}$U out of the 
core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
as start-up fuel. They concluded that the transition to thorium fuel cycle can
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.

@@

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	heuer2014towards,fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
	zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} specifically with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed scenarios were selected:

@@

This present paper is organized as follows: after an introduction about 
\gls{MSR} systems, the model description is discussed in section \ref{Model-description}. 
Methodology and tools is descried in section \ref{Methodology-and-tools}. Extraction and feed mechanisms 
are addressed in section  \ref{Feed-and-extraction-rates}. Section \ref{Results-and-discussion} focuses on the results and discussion. 
Finally, section \ref{Conclusion} highlights the conclusions.
